\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed

### 2015-03-03 Paper_JFM/grass.tex
Added A folder for JFM Paper

\documentclass[aps,prl,reprint,twocolumn,superscriptaddress,sort&compress,10pt]{revtex4-1}  % for review and submission
% \documentclass[aps,preprint,12pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\graphicspath{ {images/}{images/Growth_Rate_Cont_Plots/} }
\newcommand{\bx}{{\boldsymbol{\hat{x}}}}
\newcommand{\bn}{{\boldsymbol{\hat{n}}}}
\newcommand{\bt}{{\boldsymbol{\hat{t}}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}
\newcommand{\hg}{h_g}
\newcommand{\Rey}{{R}}
\newcommand{\Ndg}{\tilde{N}_g}
\newcommand{\monami}{\textit{monami}}
\newcommand{\ubl}{U_\text{bl}}
\newcommand{\words}[1]{\textbf{(#1)~}}
% \newcommand{\words}[1]{{}}

@@

\definecolor{tableShade}{gray}{0.8}

\begin{document}
\title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
% \author{L. Mahadevan}
% \affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi}
\affiliation{OIST Graduate University, Okinawa 904-0495, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

\words{86} Although \monami ~is manifest in the motion of the grass, the drag exerted by the grass bed on the flow is central to the hypothesized instability. 
The instability and the resulting flow structures persist in lab experiments even when flexible grass mimics are replaced by rigid dowels \cite{Ghisal02,Nepf06}. 
Therefore, to develop the essential mathematical model, we assume the grass blades to be rigid, on average oriented vertically.
We show that the drag of the grass results in an instability mode different from the Kelvin-Helmholtz instability.
\begin{figure}
\includegraphics[scale=1]{Grass_Base_Nepf_shear}
% \includegraphics[width=15cm]{Grass_Base_Nepf_shear}
\caption{
\words{111} Schematic setup and comparison of our steady flow profile with that from the experiments in ref. \cite{Nepf04} (Case I from Table 1) %  with 1250 plants/m$^2$, plant height = 13.7$\pm 0.2$ cm and blade width of 0.64 cm)
 and its approximation with $U_0=7.28$ cm/s and $\delta = 5.02$ cm in our model. The grass extends up to $y=\hg$ in the water column of depth $2H$. 
The steady velocity profile can be decomposed into a parabolic profile in the unvegetated region, a uniform profile deep within the vegetation, and a boundary layer of thickness $\delta$ near the grass top. 
The dependence of the boundary layer thickness (estimated as $|U/U_y|$ at $y=\hg$ from the numerical solution of \eqref{base_equ}) on the vegetation density parameter $\ReyNdg$ is shown in the inset.
}
\label{basicflow}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[]{Critical_Re_vs_delta_noshear} \\
\vspace{-6mm} \hspace{-3mm}
\includegraphics[]{K_vs_shear_width_noshear}
% \includegraphics[width=12cm]{Critical_Re_vs_delta_noshear} \\
% \vspace{-6mm} \hspace{-5mm}
% \includegraphics[width=12cm]{K_vs_shear_width_noshear}
\end{center}
\caption{
\words{105} Critical Reynolds number (top) and the corresponding marginally stable wave number (bottom) for different submergence ratio as a function of vegetation density parametrized by the boundary layer thickness. 
Parameters from experiments reported in ref. \cite{Ghisal02} to exhibit or suppress synchronous waving are also included in the top panel. 
Inset compares experimental observations of the experimentally measured dominant frequency $f_o$ (in Hz) with the predictions $f_p=\text{Im}(\sigma)$ from the solution of ~\eqref{Orr-somerfield}. 
The experimental data in the inset is obtained from refs. \cite{Ghisal02} (Ghisalberti) and \cite{Vivoni98} (Vivoni). 
In order to estimate the $\Rey$ for these experiments, a representative value of $\mu=0.1$ Pa~s was assumed.
}
\label{Re_vs_delta}
\end{figure}

@@

\begin{table*}
% \footnotesize
\rowcolors{3}{tableShade}{white}  %% start alternating shades from 3rd row
\renewcommand{\arraystretch}{1.2}
 \begin{tabular}{l|c|c|c}
			& Kelvin-Helmholtz 				& Mode 1 		& Mode 2 \\ \hline
 Base velocity profile 	& $U(y) = U_0 \tanh(y/\delta)$			& \multicolumn{2}{c}{Equation \eqref{base_equ}} \\
 Domain 		& $-\infty < y < \infty$			& \multicolumn{2}{c}{$-1<y<1$} \\
 Inflection point	& exists at $y=0$				& \multicolumn{2}{c}{$U''(y)$ discontinuous at $y=\hg$} \\
 Shear layer thickness	& $\delta$					& \multicolumn{2}{c}{$\delta \sim  H\left(\Rey \Ndg \right)^{-1/3}$} \\
 Linearized dynamics	& $\left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi$		& \multicolumn{2}{c}{Equation \eqref{Orr-somerfield}} \\
 Dense grass limit &  & Equation \eqref{eqn:mode1asymp} & Equation \eqref{eqn:mode2asymp}  \\
 Critical parameters	& none						& $\Rey \propto \Ndg^{1/2}$ 	& $\Rey \propto \Ndg$ \\
 Most unstable $k$ as $\delta \to 0$	& $\propto H/\delta$		& $\propto H/\delta$	& $O(1)$ \\
 Mode localized?	& yes, near $y=0$				& yes, near $y=\hg$			& no, spans water column
 \end{tabular}
 \caption{\words{17} Comparison between Kelvin-Helmholtz instability and the two unstable modes resulting from solution of \ref{Orr-somerfield}.}
 \label{tab:comparison}
\end{table*}
\words{140} To better understand the instability mechanism, we consider the dependence of the fastest growing wavenumber on $\delta$.
The fastest growing wavenumber first increases proportional to $H/\delta$, but at a critical $\delta$ discontinuously jumps and remains $O(1)$ (see Fig.~\ref{Re_vs_delta}). 
To aid in explaining this behavior, we show heat maps of Re$(\sigma)$ as a function of $\Rey$ and $k$, for different $\hg/H$ and $\Ndg$ in Fig.~\ref{K_Re_sigma_set3}. 
The smallest $\Rey$ on the neutral curve (Re$(\sigma)=0$) sets the threshold. 
We observe that as $\Ndg$ increases, the unstable region splits into two; we refer to the region with the higher $k$ as ``Mode 1'', and the one with the lower $k$ as ``Mode 2''. 
The unstable region for Mode 1, depending on $\hg/H$ either recedes to higher $\Rey$ or shrinks to zero size, as the vegetation density increases, causing the most unstable mode to transition discontinuously.

\words{117} The distinct asymptotic behavior of the two modes as $\Ndg \gg 1$ distinguishes it from the Kelvin-Helmholtz instability. 
Mode 1 asymptotically localizes to the boundary layer near the grass top, and exhibits an asymptotic behavior with $k \sim H/\delta$, and $\Rey \sim H/\delta$ (or $\Rey \propto {\Ndg}^{1/2}$) at the threshold. 
This limit can be understood by asymptotically estimating the sizes of the terms in ~\eqref{Orr-somerfield} using $D\sim H/\delta$, $\sigma \sim H/\delta$, and $\ubl \sim \delta/H$; the magnitude of the advection term is $\Rey (H/\delta)^3$  (or $\Rey^2 \Ndg$), and the viscous and the vegetation drag term in the boundary layer are $(\delta/H)^{-4}$ (or $(\Rey \Ndg)^{4/3})$. 
The terms balance when $\Rey \sim H/\delta$ (or $\Rey \sim {\Ndg}^{1/2}$), simplifying ~\eqref{Orr-somerfield} to
\begin{align}
(D^2-k^2)^2 \phi- 2 \Rey \Ndg D( SUD\phi) = \sigma \Rey (D^2-k^2)\phi,
\label{eqn:mode1asymp}
\end{align} 
\words{93} in a region of thickness O($\delta$) near $y=\hg$.
We expect identical asymptotic behavior for a fixed relative magnitude of the terms on the r.h.s. to those on the l.h.s. of \eqref{eqn:mode1asymp}, which is $(\Rey \delta/H)^{3/2}$ (or $\Rey/\Ndg^{1/2}$).
Therefore the threshold obtained for Mode 1 is $\Rey \propto H/\delta$ (or $\Rey \propto \Ndg^{1/2}$) explaining the numerically observed asymptote (see Fig.~\ref{Re_vs_delta}). 
This analysis also concludes that the mode structure is self-similar over the length scale $\delta$ for fixed $\Rey/\Ndg^{1/2}$; the verification of this idea is shown in Fig.~\ref{Asymptotic_mode} (inset).

\words{45} Similarly, the threshold condition for Mode 2 is numerically observed to be $\Rey \propto ({\delta}/{H})^{-3/2}$ (or $\Rey \propto \Ndg$) for $k\sim O(1)$, shown in Fig.~\ref{Re_vs_delta}, which can be understood by assuming $\Rey \gg 1$ but fixed $\Rey/\Ndg \sim O(1)$.
% Note that for large $\Ndg$, the non-dimensional steady flow velocity inside the vegetation is $U_g \sim (\Rey \Ndg)^{-1/2}$. 
In this limit ~\eqref{Orr-somerfield} simplifies to 
\begin{align}
\begin{split}
\sigma\left(D^2-k^2\right)\phi = -2{(\Ndg/\Rey)^{1/2}}D^2\phi,  \quad &\text{ for $y<\hg$}  \\
\left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi, \quad &\text{ for $y>\hg$}.
\end{split}
\label{eqn:mode2asymp}
\end{align}
\begin{figure}
\includegraphics[]{Asymptotic_noshear}
% \includegraphics[width=12cm]{Asymptotic_noshear}
\caption{
\words{75} Plot of the neutral Mode 1 (solid) and Mode 2 (dashed) shape $|\phi|$ in the limit of small $\delta/H$ for $\hg/H=0.2$. 
% Mode 1 is shown in solid and Mode 2 is shown in dashed. The parameters for Mode 2 shapes are chosen such that $\Rey \gg 1$, $\Ndg \gg 1$ (specified in terms of $\delta/H$) but $\Rey/\Ndg = O(1)$. 
The approach of mode shapes to each other for these small values of $\delta/H$ indicates that the dense vegetation asymptote is reached. 
Mode 1 shapes appear self-similar in shape as $\delta\to 0$.
Inset shows rescaled $|\phi|$ for Mode 1 as a function of $(y-\hg)/\delta$ approach a universal shape, indicating that an asymptotic limit has been reached. 
% The limit is not yet reached for the case $\delta/H = 0.005$ due to the influence of bottom boundary; the vegetation height in this case is comparable to the boundary layer thickness.
}
\label{Asymptotic_mode}
\end{figure}
\words{54} Since $\Rey/\Ndg$ is the only remaining parameter in \eqref{eqn:mode2asymp}, the mode shape converges in the aforementioned limit, in agreement with our numerical results shown in Fig.~\ref{Asymptotic_mode}. 
The parameter $\Rey/\Ndg$ also sets the threshold, leading to the asymptotic behavior $\Rey \propto \Ndg$ (or $\Rey \sim ({\delta}/{H})^{-3/2}$; see Fig.~\ref{Re_vs_delta} for comparison with numerical results).
% We interpret Mode 2 as the instability of an inviscid fluid, with the vegetation modeled by a continuum drag field, and for which the boundary layer near the grass top plays no role. 
% On the other hand, Mode 1 asymptotically localizes to the boundary layer near the grass tip, and exhibits a different asymptotic behavior with $k \sim O(H/\delta)$, and $\Rey \sim (H/\delta)$ (or $\Rey \propto {\Ndg}^{1/2}$) at the threshold.

@@

\acknowledgments
MMB was hosted by Brown University during this work and was supported by the OIST Graduate University with subsidy funding from the Cabinet Office, Japan. We thank Heidi Nepf, Marco Ghisalberti, and L. Mahadevan for helpful discussions.
\bibliography{Grass}{}
% \bibliographystyle{plain}
\bibliographystyle{aipauth4-1}
\end{document}

>>>>

%\documentclass[aps,prl,reprint,twocolumn,superscriptaddress,sort&compress,10pt]{revtex4-1}  % for review and submission
% \documentclass[aps,preprint,12pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\documentclass{jfm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\graphicspath{ {../Paper/images/}{../Paper/images/Growth_Rate_Cont_Plots/} }
\newcommand{\bx}{{\boldsymbol{\hat{x}}}}
\newcommand{\bn}{{\boldsymbol{\hat{n}}}}
\newcommand{\bt}{{\boldsymbol{\hat{t}}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}
\newcommand{\hg}{h_g}
%\newcommand{\Rey}{{R}}
\newcommand{\Ndg}{\tilde{N}_g}
\newcommand{\monami}{\textit{monami}}
\newcommand{\ubl}{U_\text{bl}}
\newcommand{\words}[1]{\textbf{(#1)~}}
% \newcommand{\words}[1]{{}}

@@

\definecolor{tableShade}{gray}{0.8}
\title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
% \author{L. Mahadevan}
% \affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi}
\affiliation{OIST Graduate University, Okinawa 904-0495, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

\begin{document}
\maketitle

@@

\words{86} Although \monami ~is manifest in the motion of the grass, the drag exerted by the grass bed on the flow is central to the hypothesized instability. 
The instability and the resulting flow structures persist in lab experiments even when flexible grass mimics are replaced by rigid dowels \cite{Ghisal02,Nepf06}. 
Therefore, to develop the essential mathematical model, we assume the grass blades to be rigid, on average oriented vertically.
We show that the drag of the grass results in an instability mode different from the Kelvin-Helmholtz instability.
\begin{figure}
\includegraphics[scale=1]{Grass_Base_Nepf_shear}
% \includegraphics[width=15cm]{Grass_Base_Nepf_shear}
\caption{
\words{111} Schematic setup and comparison of our steady flow profile with that from the experiments in ref. \cite{Nepf04} (Case I from Table 1) %  with 1250 plants/m$^2$, plant height = 13.7$\pm 0.2$ cm and blade width of 0.64 cm)
 and its approximation with $U_0=7.28$ cm/s and $\delta = 5.02$ cm in our model. The grass extends up to $y=\hg$ in the water column of depth $2H$. 
The steady velocity profile can be decomposed into a parabolic profile in the unvegetated region, a uniform profile deep within the vegetation, and a boundary layer of thickness $\delta$ near the grass top. 
The dependence of the boundary layer thickness (estimated as $|U/U_y|$ at $y=\hg$ from the numerical solution of \eqref{base_equ}) on the vegetation density parameter $\ReyNdg$ is shown in the inset.
}
\label{basicflow}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[]{new_graph_R_vs_delta} \\
\vspace{-5mm} \hspace{-3mm}
\includegraphics[]{K_vs_shear_width_noshear}
% \includegraphics[width=12cm]{Critical_Re_vs_delta_noshear} \\
% \vspace{-6mm} \hspace{-5mm}
% \includegraphics[width=12cm]{K_vs_shear_width_noshear}
\end{center}
\caption{
\words{105} Critical Reynolds number (top) and the corresponding marginally stable wave number (bottom) for different submergence ratio as a function of vegetation density parametrized by the boundary layer thickness. 
Parameters from experiments reported in ref. \cite{Ghisal02} to exhibit or suppress synchronous waving are also included in the top panel. 
Inset compares experimental observations of the experimentally measured dominant frequency $f_o$ (in Hz) with the predictions $f_p=\text{Im}(\sigma)$ from the solution of ~\eqref{Orr-somerfield}. 
The experimental data in the inset is obtained from refs. \cite{Ghisal02} (Ghisalberti) and \cite{Vivoni98} (Vivoni). 
In order to estimate the $\Rey$ for these experiments, a representative value of $\mu=0.1$ Pa~s was assumed.
}
\label{Re_vs_delta}
\end{figure}

@@

\begin{table*}
% \footnotesize
\rowcolors{3}{tableShade}{white}  %% start alternating shades from 3rd row
\renewcommand{\arraystretch}{1.2}
 \begin{tabular}{l|c|c|c}
			& Kelvin-Helmholtz 				& Mode 1 		& Mode 2 \\ \hline
 Base velocity profile 	& $U(y) = U_0 \tanh(y/\delta)$			& \multicolumn{2}{c}{Equation \eqref{base_equ}} \\
 Domain 		& $-\infty < y < \infty$			& \multicolumn{2}{c}{$-1<y<1$} \\
 Inflection point	& exists at $y=0$				& \multicolumn{2}{c}{$U''(y)$ discontinuous at $y=\hg$} \\
 Shear layer thickness	& $\delta$					& \multicolumn{2}{c}{$\delta \sim  H\left(\Rey \Ndg \right)^{-1/3}$} \\
 Linearized dynamics	& $\left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi$		& \multicolumn{2}{c}{Equation \eqref{Orr-somerfield}} \\
 Dense grass limit &  & Equation \eqref{eqn:mode1asymp} & Equation \eqref{eqn:mode2asymp}  \\
 Critical parameters	& none						& $\Rey \propto \Ndg^{2}$ 	& $\Rey \propto \Ndg$ \\
 Most unstable $k$ as $\delta \to 0$	& $\propto H/\delta$		& $\propto H/\delta$	& $O(1)$ \\
 Mode localized?	& yes, near $y=0$				& yes, near $y=\hg$			& no, spans water column
 \end{tabular}
 \caption{\words{17} Comparison between Kelvin-Helmholtz instability and the two unstable modes resulting from solution of \ref{Orr-somerfield}.}
 \label{tab:comparison}
\end{table*}
\words{140} To better understand the instability mechanism, we consider the dependence of the fastest growing wavenumber on $\delta$.
The fastest growing wavenumber first increases proportional to $H/\delta$, but at a critical $\delta$ discontinuously jumps and remains $O(1)$ (see Fig.~\ref{Re_vs_delta}). 
To aid in explaining this behavior, we show heat maps of Re$(\sigma)$ as a function of $\Rey$ and $k$, for different $\hg/H$ and $\Ndg$ in Fig.~\ref{K_Re_sigma_set3}. 
The smallest $\Rey$ on the neutral curve (Re$(\sigma)=0$) sets the threshold. 
We observe that as $\Ndg$ increases, the unstable region splits into two; we refer to the region with the higher $k$ as ``Mode 1'', and the one with the lower $k$ as ``Mode 2''. 
The unstable region for Mode 1, depending on $\hg/H$ either recedes to higher $\Rey$ or shrinks to zero size, as the vegetation density increases, causing the most unstable mode to transition discontinuously.

\words{117} The distinct asymptotic behavior of the two modes as $\Ndg \gg 1$ distinguishes it from the Kelvin-Helmholtz instability. 
Mode 1 asymptotically localizes to the boundary layer near the grass top, and exhibits an asymptotic behavior with $k \sim H/\delta$, and $\Rey (\sim H/\delta)^2$ (or $\Rey \propto {\Ndg}^{2}$) at the threshold. 
This limit can be understood by asymptotically estimating the sizes of the terms in ~\eqref{Orr-somerfield} using $D\sim H/\delta$, $\sigma \sim O(1)$, and $\ubl \sim \delta/H$; the magnitude of the advection term is $\Rey (H/\delta)^2$  (or $\Rey^{5/3} \Ndg^{2/3}$), and the viscous and the vegetation drag term in the boundary layer are $(\delta/H)^{-4}$ (or $(\Rey \Ndg)^{4/3})$. 
The terms balance when $\Rey \sim (H/\delta)^2$ (or $\Rey \sim {\Ndg}^{2}$). Using the boundary layer co-ordinate $\eta = y/\delta$, velocity scaling 
$U(y) = (\delta/H)\bar{U}(\eta)$ and scaling of wavenumber $k = (H/\delta) \bar{k}$ in the boundary layer ~\eqref{Orr-somerfield} simplifies to
\begin{equation}
\begin{split}
\left(\bar{D}^2 -\bar{k}^{2} \right)^2\phi &= (\Rey/\Ndg^2)^{1/3} \left[ \left({\sigma}+i\bar{k}\bar{U}\right) \left(\bar{D}^2-\bar{k}^2\right) -i\bar{k}\bar{U}_{\eta\eta}\right]\phi \\
&+\bar{D}\left(2S \bar{U} D \phi\right),
\label{eqn:mode1asymp}
\end{split}
\end{equation}

\words{93} in a region of thickness O($\delta$) near $y=\hg$. Since $(\Rey/\Ndg^2)$ is the only remaining parameter in \eqref{eqn:mode1asymp}, the mode shape and soultion will converge in the limit of $R \sim \Ndg^2$, confirming our numerial finding.
%We expect identical asymptotic behavior for a fixed relative magnitude of the terms on the r.h.s. to those on the l.h.s. of \eqref{eqn:mode1asymp}, which is $(\Rey \delta/H)^{3/2}$ (or $\Rey/\Ndg^{1/2}$).
%Therefore the threshold obtained for Mode 1 is $\Rey \propto H/\delta$ (or $\Rey \propto \Ndg^{1/2}$) explaining the numerically observed asymptote (see Fig.~\ref{Re_vs_delta}). 
This analysis also concludes that the mode structure is self-similar over the length scale $\delta$ for fixed $\Rey/\Ndg^{2}$; the verification of this idea is shown in Fig.~\ref{Asymptotic_mode} (inset).

\words{45} Similarly, the threshold condition for Mode 2 is numerically observed to be $\Rey \propto ({\delta}/{H})^{-3/2}$ (or $\Rey \propto \Ndg$) for $k\sim O(1)$, shown in Fig.~\ref{Re_vs_delta}, which can be understood by assuming $\Rey \gg 1$ but fixed $\Rey/\Ndg \sim O(1)$.
% Note that for large $\Ndg$, the non-dimensional steady flow velocity inside the vegetation is $U_g \sim (\Rey \Ndg)^{-1/2}$. 
In this limit ~\eqref{Orr-somerfield} simplifies to 
\begin{align}
\begin{split}
\sigma\left(D^2-k^2\right)\phi = -2{(\Ndg/\Rey)^{1/2}}D^2\phi,  \quad &\text{ for $y<\hg$}  \\
\left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi, \quad &\text{ for $y>\hg$}.
\end{split}
\label{eqn:mode2asymp}
\end{align}
\begin{figure}
\includegraphics[]{Asymptotic_noshear}
% \includegraphics[width=12cm]{Asymptotic_noshear}
\caption{
\words{75} Plot of the neutral Mode 1 (solid) and Mode 2 (dashed) shape $|\phi|$ in the limit of small $\delta/H$ for $\hg/H=0.2$. 
% Mode 1 is shown in solid and Mode 2 is shown in dashed. The parameters for Mode 2 shapes are chosen such that $\Rey \gg 1$, $\Ndg \gg 1$ (specified in terms of $\delta/H$) but $\Rey/\Ndg = O(1)$. 
The approach of mode shapes to each other for these small values of $\delta/H$ indicates that the dense vegetation asymptote is reached. 
Mode 1 shapes appear self-similar in shape as $\delta\to 0$.
Inset shows rescaled $|\phi|$ for Mode 1 as a function of $(y-\hg)/\delta$ approach a universal shape, indicating that an asymptotic limit has been reached. 
% The limit is not yet reached for the case $\delta/H = 0.005$ due to the influence of bottom boundary; the vegetation height in this case is comparable to the boundary layer thickness.
}
\label{Asymptotic_mode}
\end{figure}
\words{54} Similarly here $\Rey/\Ndg$ is the only remaining parameter in \eqref{eqn:mode2asymp}, the mode shape converges in the aforementioned limit, in agreement with our numerical results shown in Fig.~\ref{Asymptotic_mode}. 
The parameter $\Rey/\Ndg$ also sets the threshold, leading to the asymptotic behavior $\Rey \propto \Ndg$ (or $\Rey \sim ({\delta}/{H})^{-3/2}$; see Fig.~\ref{Re_vs_delta} for comparison with numerical results).
% We interpret Mode 2 as the instability of an inviscid fluid, with the vegetation modeled by a continuum drag field, and for which the boundary layer near the grass top plays no role. 
% On the other hand, Mode 1 asymptotically localizes to the boundary layer near the grass tip, and exhibits a different asymptotic behavior with $k \sim O(H/\delta)$, and $\Rey \sim (H/\delta)$ (or $\Rey \propto {\Ndg}^{1/2}$) at the threshold.

@@

\acknowledgments
MMB was hosted by Brown University during this work and was supported by the OIST Graduate University with subsidy funding from the Cabinet Office, Japan. We thank Heidi Nepf, Marco Ghisalberti, and L. Mahadevan for helpful discussions.

% Note the spaces between the initials
\bibliography{Grass.bib}{}
\bibliographystyle{jfm}
%\bibliography{Grass}{}
% \bibliographystyle{plain}
%\bibliographystyle{aipauth4-1}
\end{document}
